### 2012-09-27 doc/prelim/document/chapters/research_proposal/research_proposal.tex
adding heat equation setup figure

\subsection{MCSA Application to Finite Element Problems}
\label{subsec:mcsa_finite_element}

>>>>

\subsection{MCSA Application to Finite Element Problems}
\label{subsec:mcsa_finite_element}
The Epetra-based MCSA implementation has enabled the solution of
finite element problems leveraging the Panzer finite element assembly
engine, providing an initial basis for our experimental framework. To
demonstrate this, consider the 2-dimensional steady-state heat
equation:
\begin{equation}
  \boldsymbol{\nabla} \cdot k \boldsymbol{\nabla} T = Q\:,
  \label{eq:heat_equation}
\end{equation}
where $k$ is the thermal conductivity, $T$ is the temperature, and $Q$
is the thermal source. We can write the heat equation in weak form
using Eq~(\ref{eq:fe_weak_form}):
\begin{equation}
  \int_{\Omega} \boldsymbol{\nabla}^T \ve{v} k \boldsymbol{\nabla} T
  d\Omega - \int_{\Omega} \ve{v}Q d\Omega - \int_{\Gamma} \ve{v}
  \bar{q} d\Gamma - \int_{\Gamma} \ve{v} k \frac{\partial T}{\partial
    n} d\Gamma= 0\:,
  \label{eq:weak_heat_equation}
\end{equation}
where the boundary conditions have now been incorporated. We can
interpret the last two integral terms as the contributions from a
fixed boundary flux source and the flux through the domain
boundary. This weak formulation can then be directly implemented
within the finite element assembly engine along with the appropriate
boundary conditions and source terms. For this example, we choose a
square Cartesian grid with boundary conditions as shown in
Figure~\ref{fig:heat_eq_setup}.
